A Recipe for Scavenging \textcolor{blue}{in Vertebrates} - the natural history of a behaviour

### 2016-07-14 response_letter.tex

We would like to thank the editor, subject editor and reviewers for their comments. By bringing attention to elements of the manuscript that require more careful communication we believe that you have helped us to significantly improve our manuscript. In this submission we have clarified these areas and added a body of work to bolster the conclusions drawn from our work. Please see below where we consider each of your points in turn.
For improved clarity in this document and in the manuscript, we have highlighted our responses in \textcolor{blue}{blue}.

\section{Recommendation by the Subject Editor (anonymous):}
Three experienced reviews have evaluated your manuscript. Two of them are extremely critical of several aspects related to to the general handcraft and novelly of the review. The third reviewer is more positive, while making substantial recommendations for improvement of the manuscript. Should you be able to address all of the reviewers comments in a much revised version of the manuscript I would happy to reconsider the manuscript for consideration in Ecography and the E4 Award. This is not a provisional acceptance, since the manuscript would need to be revised again.

\smallskip

\textcolor{blue}{As we note below, we feel our earlier manuscript did not capture the hierarchy we had in mind.This updated version is more explicit in terms of the structure where we now highlight the sections and subsections. Regarding the novelty of our manuscript, we have changed our introduction which was regarded as too similar to deValult et al. (2003) and argue our case for what we consider inevitable overlap with Beasley et al. (2015).}

### 2016-07-14 natural history of scavenging.tex
Sub sectioning carcasse availability + adding the commented bits to Facilitation part

\subsection{\textcolor{blue}{Abiotic effects on Carcass} Availability}
The environmental influence on \textcolor{blue}{carcass} availability is an aspect that greatly affects encounter rate. %but is invisible to the selective forces acting on the scavenger. 
Aspects including, primary productivity, relief, and temperature will all affect scavenging tendency.

@@

Perhaps the greatest environmental driver of scavenging tendency is that of temperature. 
his has a significant bearing on the availability and persistence of carrion.
We know from the geological record shows that the Earth has undergone radical fluctuations in temperature over time.
\textcolor{blue}{TOn land, there are a wide variety of vegetation types, from thickly forested areas to open grassland and the extent of this vegetation changes with season.}
All of these factors influence the availabiltiy of carrion.  
Moreover, oceanic productivity is also impacted by climactic conditions.

@@

\subsection{\textcolor{blue}{Biotic effects on Carcass} Availability}
Through facilitation e.g. local enhancement, adept scavengers may increase the amount of carrion mammalian carnivores feed on thus increasing their population size \citep{moleon2014inter}. 
This higher population of predators will take more prey and so produce more carcasses. Conversely, by feeding on carcasses, predators may hunt less because they are sated by carrion, ultimately reducing predation risk on their prey base \citep{moleon2014inter}.

@@

\subsection{Facilitation}
As well as competitive interactions, there are also facilitatory processes at play between vertebrate scavengers that can reduce handling time for the facilitated species. 
Some examples include vultures, hyenas and wolves opening the tough hides of ungulate carcasses that would otherwise be inaccessible to corvids and smaller mammalian carnivores \citep{selva2003scavenging,moleon2015carcass}.

@@

% Modern scavenging assemblages can be inflenced by carcass size \citep{moleon2015carcass}. 
% Larger carcasses tend to last longer and also present a more conspicuous target for a foraging scavenger which results in more species attending them \citep{moleon2015carcass}.
% This will have had implications for extinct assemblages because body size distribtions vary across different environments but also across time. 
% \cite{10.1371/journal.pone.0051925} showed Mesozoic faunal distributions may have been skewed towards larger species even when fossil biases are taken into account. 
% If this pattern is real then the scavenger assemblages during this era would have been particularly diverse.

>>>>

\subsection{Carcass Availability}
\subsubsection{\textcolor{blue}{Abiotic effects}}
The environmental influence on \textcolor{blue}{carcass} availability is an aspect that greatly affects encounter rate. %but is invisible to the selective forces acting on the scavenger. 
Aspects including, primary productivity, relief, and temperature will all affect scavenging tendency.

@@

Perhaps the greatest environmental driver of scavenging tendency is that of temperature. 
his has a significant bearing on the availability and persistence of carrion.
We know from the geological record shows that the Earth has undergone radical fluctuations in temperature over time.
\textcolor{blue}{On land, there are a wide variety of vegetation types, from thickly forested areas to open grassland and the extent of this vegetation changes with season.}
All of these factors influence the availabiltiy of carrion.  
Moreover, oceanic productivity is also impacted by climactic conditions.

@@

\subsubsection{\textcolor{blue}{Biotic effects}}
Through facilitation e.g. local enhancement, adept scavengers may increase the amount of carrion mammalian carnivores feed on thus increasing their population size \citep{moleon2014inter}. 
This higher population of predators will take more prey and so produce more carcasses.
Conversely, by feeding on carcasses, predators may hunt less because they are sated by carrion, ultimately reducing predation risk on their prey base \citep{moleon2014inter}.

\textcolor{blue}{Modern scavenging assemblages can be influenced by carcass size \citep{moleon2015carcass}. 
Larger carcasses tend to last longer and also present a more conspicuous target for a foraging scavenger which results in more species attending them \citep{moleon2015carcass}.
This will have had implications for extinct assemblages because body size distributions vary across different environments but also across time. 
\cite{10.1371/journal.pone.0051925} showed Mesozoic faunal distributions may have been skewed towards larger species even when fossil biases are taken into account. 
If this pattern is real then the scavenger assemblages during this era would have been particularly diverse.}

@@

\textcolor{blue}{\subsection{Facilitation}
As well as competitive interactions, there are also facilitatory processes at play between vertebrate scavengers that can reduce handling time for the facilitated species. 
Rather than there being a random assortment of species at a carcass, scavenging assemblages tend to be nested \citep{selva2007nested}. 
This means the species that feed on the majority of carcasses, for example vultures, are a subset of a larger community which comprises hyenas, jackals, raptors etc. \citep{sebastian2016nested}. 
In extant systems these interactions can reduce handling times for the facilitated species. 
Some examples include vultures, hyenas and wolves opening the tough hides of ungulate carcasses that would otherwise be inaccessible to corvids and smaller mammalian carnivores \citep{selva2003scavenging,moleon2015carcass}.
The availability of carcasses can be indirectly influenced by the action of scavengers. 
Through facilitation e.g. local enhancement, vultures may increase the amount of carrion mammalian carnivores feed on thus increasing their population size \citep{moleon2014inter}. 
This higher population of predators will take more prey and so produce more carcasses. Conversely, by feeding on carcasses, predators may hunt less because they are sated by carrion, ultimately reducing predation risk on their prey base \citep{moleon2014inter}.}

@@

% Modern scavenging assemblages can be influenced by carcass size \citep{moleon2015carcass}. 
% Larger carcasses tend to last longer and also present a more conspicuous target for a foraging scavenger which results in more species attending them \citep{moleon2015carcass}.
% This will have had implications for extinct assemblages because body size distributions vary across different environments but also across time. 
% \cite{10.1371/journal.pone.0051925} showed Mesozoic faunal distributions may have been skewed towards larger species even when fossil biases are taken into account. 
% If this pattern is real then the scavenger assemblages during this era would have been particularly diverse.
